\documentstyle[cprog]{report}
\includeonly{future}
\begin{document}
\setlength{\textwidth}{7.4in}
\setlength{\oddsidemargin}{1in}
\setlength{\evensidemargin}{1in}
\setlength{\topmargin}{0in}
\title{The Kamin Interpreters in C++}
\author{Tim Budd}
\maketitle
\begin{abstract}
This paper describes a series of interpreters for the languages used in the 
book ``Programming Languages: An Interpreter-Based Approach'' by Samuel 
Kamin (Addison-Wesley, 1989).  Unlike the interpreters provided by Kamin,
which are written in Pascal, 
these interpreters are written in C++.
It is my belief that the use of inheritance in C++ better
illustrates the unique features of each of the several languages.
In the Pascal versions of the interpreters the differences between the
various interpreters, although small, are scattered throughout the code.
In the C++ versions differences are produced using only the mechanism of
subclassing.  This means that the vast majority of code remains the same, 
and differences can be much more precisely isolated.

The chapters in this report correspond to the chapters in the original text.
Where motivational or background material is provided in that source it is
generally omitted here.  A major exception is in those places (chiefly
chapters 3, 7 and 8) where I have selected a syntax slightly different 
from that provided by Kamin.

The use of an Object-Oriented language for the interpreters may seem a bit
incongruous, since Object-Oriented programming is not discussed until
Chapter 7.  Nevertheless, I think the benefits of programming the
interpreters in C++ outweighs this problem.
\end{abstract}

\input{chap1}
\input{chap2}
\input{chap3}
\input{chap4}
\input{chap5}
\input{chap6}
\input{chap7}
\input{chap8}
\input{future}
\end{document}
